Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech

### 2021-03-31 RR_manuscript/Draft_RR.Rmd
:memo: - edit RR

---
title: "Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech"
runninghead: "Many analysts, one speech data set"
author:
- name: Stefano Coretta*
  num: 1
- name: Joseph V. Casillas
  num: 2
- name: Timo B. Roettger
  num: 3
address:
- num: 1
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.
- num: 2
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 3
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Stefano Coretta"
email: "s.coretta@lmu.de"
abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might can facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*

@@

- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens [numeric].
- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].

>>>>

---
title: "Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech"
runninghead: "Many analysts, one speech data set"
author:
- name: Stefano Coretta*
  num: 1
- name: Joseph V. Casillas
  num: 2
- name: Timo B. Roettger
  num: 3
address:
- num: 1
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.
- num: 2
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 3
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Stefano Coretta"
email: "s.coretta@lmu.de"
abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*

@@

- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students [numeric].
- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].

### 2021-03-31 RR_manuscript/Draft_RR.tex
:memo: - edit RR

\begin{abstract}
Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might can facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
\end{abstract}

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}

@@

\begin{itemize}
\tightlist
\item
  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens {[}numeric{]}.
\item
  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire {[}numeric{]}.
\end{itemize}

>>>>

\begin{abstract}
Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines. Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior. In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question. Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
\end{abstract}

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}

@@

\begin{itemize}
\tightlist
\item
  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students {[}numeric{]}.
\item
  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire {[}numeric{]}.
\end{itemize}
